Computing Exact Restricted Isometry Constants via\\ Mixed Integer Semidefinite Programming

### 2016-03-11 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
slightly extended proof of lemma

\begin{lemma}\label{HalfConstraint} 
The constraint $-z_j \leq X_{ij} \leq z_j$ in~\eqref{MISDP} can be substituted for all non-diagonal entries of $X$ by the stronger constraint 
\begin{equation}\label{eq:HalfConstraint}
  -\frac{1}{2}z_j \leq X_{ij} \leq \frac{1}{2}z_j.
\end{equation}
\end{lemma}
\begin{proof}
Let $X$ satisfy $\Tr(X)=1$ and $X\succeq 0$, which immediately implies $X_{ii}\geq 0$.
Since all minors of $X$ need to be nonnegative, we get that
\begin{equation*}
  X_{ij}^2 \leq  X_{ii} X_{jj} \leq \frac{1}{4}
\end{equation*}
and therefore $-1/2 \leq X_{ij} \leq 1/2$, which implies the equivalence between
$-z_j \leq X_{ij} \leq z_j$ and~\eqref{eq:HalfConstraint} for all integer values 
of $z$..
\end{proof}

>>>>

\begin{lemma}\label{HalfConstraint} 
The constraint $-z_j \leq X_{ij} \leq z_j$ in~\eqref{MISDP} can be substituted for all non-diagonal entries of $X$ by the stronger constraint 
\begin{equation}\label{eq:HalfConstraint}
  -\frac{1}{2}z_j \leq X_{ij} \leq \frac{1}{2}z_j.
\end{equation}
\end{lemma}
\begin{proof}
Let $X$ satisfy $\Tr(X)=1$ and $X\succeq 0$. Then $X_{ii}+X_{jj}\leq 1$ and nonnegativity of the diagonal 
entries imply $X_{ii}X_{jj}\leq 1/4$. 
Since all minors of $X$ need to be nonnegative, it follows that
\begin{equation*}
  X_{ij}^2 \leq  X_{ii} X_{jj} \leq \frac{1}{4}
\end{equation*}
and therefore $-1/2 \leq X_{ij} \leq 1/2$, which implies the equivalence between
$-z_j \leq X_{ij} \leq z_j$ and~\eqref{eq:HalfConstraint} for all integer values 
of $z$.
\end{proof}
